\documentclass[letterpaper,12pt]{report}
\usepackage[margin=1in]{geometry}
\usepackage{fancyhdr,tocloft,url,graphicx,float,listings,sidecap,wrapfig}
\usepackage[numbers]{natbib}
\usepackage[font=small,labelfont=bf,labelsep=period]{caption}
\usepackage{tabularx}
\usepackage{setspace}
% \usepackage{hyperref}
% \usepackage[all]{hypcap}
\usepackage{qtree,algorithm,algorithmic}
\usepackage{tcolorbox}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{times}
\usepackage[utf8]{inputenc}

\pagestyle{plain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{}
\cfoot{\thepage}


%\floatstyle{boxed}
%\restylefloat{figure}

% \hypersetup {
% 	colorlinks=false,
% 	pdfborder={0 0 0},
% }

\setcounter{secnumdepth}{3}
\renewcommand*\thesection{\arabic{section}.}
\renewcommand*\thesubsection{\thesection\arabic{subsection}.}
\renewcommand*\thesubsubsection{\thesubsection\arabic{subsubsection}.}

\setcounter{tocdepth}{3}
\renewcommand\contentsname{}				% TOC title
\renewcommand\listfigurename{}				% LOF title
\renewcommand\listtablename{}				% LOT title
\setlength\cftaftertoctitleskip{-0.5in}
\setlength\cftafterloftitleskip{-0.5in}
\setlength\cftafterlottitleskip{-0.5in}
\makeatletter
\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,fill=black,inner sep=1pt] (char) {\textcolor{white}{\small\bfseries #1}};}}

            \lstset{
                basicstyle=\ttfamily,
                breakindent=2em,
            }

\begin{document}

% \hypersetup{pageanchor=true}
%%  COVER PAGE
\input{cover}	
\clearpage

%% SIGNATURE PAGE
\input{signature}
\clearpage

% \hypersetup{pageanchor=true}
\setcounter{page}{1}
\pagenumbering{roman}
\renewcommand\arraystretch{1.5}

%% ABSTRACT
\vspace*{0.5in}
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}
Weninger, Daniel, ``PAMEx: A Compiler and Tools to Support a 
More Flexible Security Policy for Simpleflow'' Master of Software 
Engineering, May 2023, (W. Michael Petullo, Ph.D.). \\

This manuscript describes the design and implementation of PAMEx, a custom-built Linux security tool 
suite that uses several aspects of modern Linux security modules to enforce its policies. 
The tool suite uses extended attributes to define file security information, a custom Pluggable Authentication Module (PAM) 
to define actions that occur when a user authenticates on a system, 
and a custom compiler developed with Flex and Bison. PAMEx was developed as a security enhancement for SimpleFlow, 
a project that uses information flows to enforce policies. The way that PAMEx provides this enhancement to SimpleFlow 
is by being able to classify and compartmentalize file security as hierarchical levels, and non-hierarchical labels 
rather than the binary policy that SimpleFlow currently has in place. 
As a simulation, a tool was created and given the name Oracle that, when queried, 
will output a response as to if a user has access to a particular file. This paper gives an overview of the design and 
implementation choices made during the development of PAMEx and future work that could be done to maintain and improve the project. 
\clearpage

%%% ACKNOWLEDGEMENTS
\vspace*{0.5in}
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgments}
\par 
\hspace{1em}
I would like to give my sincerest gratitude and thanks to my advisor, Dr. Petullo. Without whom I would not have been able to get as far as I had or learn as much as I did during the development of my capstone project.
\clearpage

%% TABLE OF CONTENTS
\vspace*{0.5in}
\section*{Table of Contents}
\tableofcontents
\clearpage


% %% LIST OF TABLES
% \section*{List of Tables}
% \addcontentsline{toc}{section}{List of Tables}
% \listoftables
% \clearpage

%% LIST OF FIGURES
\vspace*{0.5in}
\section*{List of Figures}
\addcontentsline{toc}{section}{List of Figures}
\listoffigures
\clearpage

%% GLOSSARY
\vspace*{0.5in}
\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}
\input{glossary}
\clearpage

\setcounter{page}{1}
\pagenumbering{arabic}

\IfFileExists{section01/section}{\input{section01/section}}{}\clearpage
\IfFileExists{section03/section}{\input{section03/section}}{}\clearpage
\IfFileExists{section04/section}{\input{section04/section}}{}\clearpage
\IfFileExists{section04/section}{\input{section05/section}}{}\clearpage
\IfFileExists{section04/section}{\input{section06/section}}{}\clearpage
\IfFileExists{section04/section}{\input{section07/section}}{}\clearpage

%% BIBLIOGRAPHY
% \section*{Bibliography}
\begin{thebibliography}{14}
    \addcontentsline{toc}{section}{Bibliography}

\bibitem{jorgensen2021}
Jorgensen, Paul C. \textit{Software Testing: A Craftsmans Approach}. Auerbach Publications, 2021.

\bibitem{kung2014}
Kung, David C. \textit{Object-Oriented Software Engineering: An Agile Unified Methodology}. McGraw-Hill, 2014.

\bibitem{lauber}
Pluggable Authentication Modules (PAM), https://www.redhat.com/sysadmin/pluggable-authentication-modules-pam, last accessed 15 April 2023.

\bibitem{lacey2015}
Lacey, Mitch. \textit{The Scrum Field Guide: Practical Advice For Your First Year}. Addison-Wesley, 2015.

\bibitem{levine2009}
Levine, John. \textit{Flex \& Bison}. O'Reilly, 2009.

\bibitem{levine1995}
Levine, John R., et al. \textit{Lex \& Yacc}. O'Reilly, 1995.

\bibitem{kerneldocs}
The Linux Kernel Documentation, https://www.kernel.org/doc/html/latest/, last accessed 15 April 2023.

\bibitem{linuxpam}
Linux-Pam/Linux-Pam: Linux PAM (Pluggable Authentication Modules for Linux) Project, https://github.com/linux-pam/linux-pam, last accessed 15 April 2023.

\bibitem{man7pam}
Linux-PAM, ``pam - Pluggable Authentication Modules for Linux'', Linux-PAM Manual, Release 1.3.1, 2020.

\bibitem{natsecinfo}
Senate Select Committee on Intelligence. ``National Security Information'' Senate Select Committee on Intelligence, https://www.intelligence.senate.gov/laws/national-security-information

\bibitem{ryan2016}
Ryan Johnson, Jessie Lass, W. Michael Petullo. ``Studying Naive Users and the Insider Threat with SimpleFlow'' Proceedings of the 8th ACM CCS International Workshop on Managing Insider Security Threats, 2016.

\bibitem{scrumorg}
What is Scrum?, https://www.scrum.org/learning-series/what-is-scrum, last accessed 15 April 2023.

\bibitem{selinux}
SELinux Project, https://selinuxproject.org/, last accessed 15 April 2023.

\bibitem{man7xattr}
T. Ts'o, ``xattr - Extended attributes,'' Linux Programmer's Manual, xattr(7), 2021.

\end{thebibliography}

\clearpage

% %%% APPENDICES
% \section{Appendices}
% \label{sec:appendices}
% \clearpage

\end{document}
